COG-ED Manuscript

### 2021-10-19 06_Paper/COG-ED/Manuscript.Rmd
implemented rmANOVA for more hypotheses

  knitr::opts_chunk$set(echo = TRUE)
  library(bibtex)
  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(nlme)         # fitting nonlinear mixed-effects model
  library(ez)           # compute repeated measures ANOVA
  library(emmeans)      # for custom contrasts in ANOVAs

@@

# FIXME what about RT preprocessing?
  # correct / postcorrect     *see Westbrook et al. 2013, table 1: correct trials
  # log-transformation
  # valid answers: false alarm vs. missing -> plausible responses

@@

      # define contrasts

      contrasts(h1b_data$level) <- cbind(c(1,-1,0), c(0,1,-1), c(1,0,-1))

@@

      hypothesis1b_anova <- summary(aov(h1b_data$meanrt ~ h1b_data$level))
      hypothesis1b_posthoc <- TukeyHSD(aov(h1b_data$meanrt ~ h1b_data$level))
      remove(h1b_data)

@@

      # define contrasts

      contrasts(h1c_data$level) <- cbind(c(1,-1,0,0), c(0,1,-1,0), c(0,0,1,-1),
                                         c(1,0,-1,0), c(1,0,0,-1), c(0,1,0,-1))

@@

      hypothesis1c1_anova <- summary(aov(h1c_data$mental ~ h1c_data$level))
      hypothesis1c1_posthoc <- TukeyHSD(aov(h1c_data$mental ~ h1c_data$level))

      hypothesis1c2_anova <- summary(aov(h1c_data$physical ~ h1c_data$level))
      hypothesis1c2_posthoc <- TukeyHSD(aov(h1c_data$physical ~ h1c_data$level))

      hypothesis1c3_anova <- summary(aov(h1c_data$time ~ h1c_data$level))
      hypothesis1c3_posthoc <- TukeyHSD(aov(h1c_data$time ~ h1c_data$level))

      hypothesis1c4_anova <- summary(aov(h1c_data$performance ~ h1c_data$level))
      hypothesis1c4_posthoc <- TukeyHSD(aov(h1c_data$performance ~ h1c_data$level))

      hypothesis1c5_anova <- summary(aov(h1c_data$effort ~ h1c_data$level))
      hypothesis1c5_posthoc <- TukeyHSD(aov(h1c_data$effort ~ h1c_data$level))

      hypothesis1c6_anova <- summary(aov(h1c_data$frustration ~ h1c_data$level))
      hypothesis1c6_posthoc <- TukeyHSD(aov(h1c_data$frustration ~ h1c_data$level))

      # TODO: see H1a. 
      num_vars <- c("mental", "physical", "time", "performance", "effort", "frustration")
      h1c_data[num_vars] <- lapply(h1c_data[num_vars], as.numeric)
      hypothesis1c_rmanova <- ezANOVA(h1c_data, dv = mental, wid = subject, within = level, 
                                       type = 3, return_aov = T)
      #...

      # We may also run a rmMANOVA
      # https://cran.r-project.org/web/packages/MANOVA.RM/vignettes/Introduction_to_MANOVA.RM.html
      library(MANOVA.RM)
      # we need to convert our data frame to clean wide or long format

      remove(h1c_data)

@@

  # define contrasts

  contrasts(h2a_data$level) <- cbind(c(1,-1,0,0), c(0,1,-1,0), c(0,0,1,-1),
                                     c(1,0,-1,0), c(1,0,0,-1), c(0,1,0,-1))

  hypothesis2a_anova <- summary(aov(h2a_data$sv ~ h2a_data$level))
  hypothesis2a_posthoc <- TukeyHSD(aov(h2a_data$sv ~ h2a_data$level))

@@

>>>>

  knitr::opts_chunk$set(echo = TRUE)
  library(bibtex)
  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(nlme)         # fitting nonlinear mixed-effects model
  library(afex)         # compute repeated measures ANOVA, "afex" package
  library(emmeans)      # for custom contrasts in ANOVAs, "emmeans" package

@@

@@

@@

      hypothesis1b_rmanova <- afex::aov_ez(data = h1b_data,
                                           dv = "meanrt",
                                           id = "subject",
                                           within = "level",
                                           type = 3,
                                           include_aov = TRUE)

      hypothesis1b_emm <- emmeans(object = hypothesis1b_rmanova$aov,
                                  specs = "level")
      hypothesis1b_contrasts <- pairs(hypothesis1b_emm)

      remove(h1b_data)

@@

@@

      hypothesis1c_mental_rmanova <- afex::aov_ez(data = h1c_data,
                                                  dv = "mental", id = "subject", within = "level",
                                                  type = 3, include_aov = TRUE)
      hypothesis1c_physical_rmanova <- afex::aov_ez(data = h1c_data,
                                                  dv = "physical", id = "subject", within = "level",
                                                  type = 3, include_aov = TRUE)
      hypothesis1c_time_rmanova <- afex::aov_ez(data = h1c_data,
                                                  dv = "time", id = "subject", within = "level",
                                                  type = 3, include_aov = TRUE)
      hypothesis1c_performance_rmanova <- afex::aov_ez(data = h1c_data,
                                                  dv = "performance", id = "subject", within = "level",
                                                  type = 3, include_aov = TRUE)
      hypothesis1c_effort_rmanova <- afex::aov_ez(data = h1c_data,
                                                  dv = "effort", id = "subject", within = "level",
                                                  type = 3, include_aov = TRUE)
      hypothesis1c_frustration_rmanova <- afex::aov_ez(data = h1c_data,
                                                  dv = "frustration", id = "subject", within = "level",
                                                  type = 3, include_aov = TRUE)

      hypothesis1c_emm <- emmeans(object = hypothesis1c_mental_rmanova$aov, specs = "level")
      hypothesis1c_mental_contrasts <- pairs(hypothesis1c_emm)

      hypothesis1c_emm <- emmeans(object = hypothesis1c_physical_rmanova$aov, specs = "level")
      hypothesis1c_physical_contrasts <- pairs(hypothesis1c_emm)

      hypothesis1c_emm <- emmeans(object = hypothesis1c_time_rmanova$aov, specs = "level")
      hypothesis1c_time_contrasts <- pairs(hypothesis1c_emm)

      hypothesis1c_emm <- emmeans(object = hypothesis1c_performance_rmanova$aov, specs = "level")
      hypothesis1c_peformance_contrasts <- pairs(hypothesis1c_emm)

      hypothesis1c_emm <- emmeans(object = hypothesis1c_effort_rmanova$aov, specs = "level")
      hypothesis1c_effort_contrasts <- pairs(hypothesis1c_emm)

      hypothesis1c_emm <- emmeans(object = hypothesis1c_frustration_rmanova$aov, specs = "level")
      hypothesis1c_frustration_contrasts <- pairs(hypothesis1c_emm)

      remove(h1c_data, hypothesis1c_emm)

@@

  hypothesis2a_rmanova <- afex::aov_ez(data = h2a_data,
                                       dv = "sv", id = "subject", within = "level",
                                       type = 3, include_aov = TRUE)

  hypothesis2a_emm <- emmeans(object = hypothesis2a_rmanova$aov,
                              specs = "level")
  hypothesis2a_contrasts <- pairs(hypothesis2a_emm)

@@

  # create an index for the rows in which the participant ID changes
